>

### 2019-10-28 manuscript/manuscript.Rmd
Correct the distance decay utility parameter

We calculate a set of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
the park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in the Alameda County (Oakland), California using
this utility specification, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.98$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. In the absence 
of park trip destination choice coefficients in New York City, we adopt these
previous estimates.

>>>>

We calculate a set of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
the park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in the Alameda County (Oakland), California using
this utility specification, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. In the absence 
of park trip destination choice coefficients in New York City, we adopt these
previous estimates.
